GNSS-based displacement detection using Bayesian inference for deformation monitoring

### 2020-11-23 paper/manuscript-iot.tex
proof reading 3 complete

	% As a general rule, do not put math, special symbols or citations
	% in the abstract or keywords.
	\begin{abstract}
For decades, displacement detection based on the Global navigation satellite system (GNSS) has increasingly been important for a wide range of applications, from landslide monitoring, subsidence survey, to industrial measurement. 
Most of the GNSS-based displacement detection methods in these applications are based on GNSS long-term static positioning results.
With the development of Internet of Things (IoT), high-precision GNSS positioning, and GNSS related transmission protocol, kinematic positioning results can be transmitted to the cloud in real-time.
However, due to the influence of measurement noise, it is still a challenge to identify and extract displacement from GNSS kinematic positioning results in a short time.
To resolve this, we propose a novel displacement detection approach with the purpose of identifying and extracting displacement from GNSS kinematic positioning in a short time.
Specifically, we use the Bayesian inference model to obtain the displacement change time from the coordinate time series of GNSS kinematic positioning. 
%The likelihood function of the observation and the prior distribution of the parameters to be estimated are provided.
%Finally, Bayesian inference was implemented by Markov Chain Monte Carlo (MCMC) sampling.
By investigating the posterior distribution of the designed change point parameter, we can identify the change points.
Furthermore, we derive the mean value from the posterior distribution of the mean parameter, and further obtain the displacement.
Results from simulation and field experiments have demonstrated the effectiveness and flexibility of the proposed method.
For significant displacement, it can be clearly identified; for small displacement, it can be identified by adding an interval constraint prior. The accuracy of up-displacement extraction from GNSS real-time kinematic positioning can reach within 2 mm in 15 minutes.
	\end{abstract}

@@

	\section{Introduction}
	% The very first letter is a 2 line initial drop letter followed
	% by the rest of the first word in caps.
	% 
	% form to use if the first word consists of a single letter:
	% \IEEEPARstart{A}{demo} file is ....
	% 
	% form to use if you need the single drop letter followed by
	% normal text (unknown if ever used by the IEEE):
	% \IEEEPARstart{A}{}demo file is ....
	% 
	% Some journals put the first two words in caps:
	% \IEEEPARstart{T}{his demo} file is ....
	% 
	% Here we have the typical use of a "T" for an initial drop letter
	% and "HIS" in caps to complete the first word.
	\label{intro}
	%全球定位系统系统的应用-》位移探测
	%在自然灾害监测，或者工业测量等领域，GNSS被用于位移探测。
	%传统测量仪器的弊端，GNSS位移探测的优势。
	%GNSS在位移探测中扮演的角色，以及位移探测的要求
	%目前人们对于基于GNSS位移探测的研究更过的关注与如何提高定位的精度，而忽略了如何从GNSS获取的坐标序列中识别并提取位移。
	\IEEEPARstart{I}{n}  recent decades, the Global navigation satellite system (GNSS) has been widely used in surveying\cite{barry2011surveying}, and civil aviation\cite{iatsouk2004development}, and autonomous vehicle\cite{kuutti2018survey} as a positioning method. 
	Besides, as a displacement detection method in deformation monitoring, GNSS has been applied to landslide monitoring\cite{awange2012environmental}, subsidence survey\cite{bian2014monitoring}, industrial measurement\cite{pavasovic2011application}, and other fields. 
	Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high precision, and weather independence\cite{shen2019a}. 
	%随着物联网通信技术标准的制订和创新，高精度定位技术，例如RTK，PPP，以及GNSS传输协议NTRIP的发展，GNSS定位结果可以被实时传输到云端。
	With the development of the Internet of things (IoT), GNSS high-precision positioning technology, and GNSS enhanced information transmission protocol, high-precision GNSS positioning results can be transmitted to the cloud in real-time\cite{mei2019survey}.
	%Displacement detection involves displacement identification and extraction. 
	GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results\cite{abidin2004use,rs12203375}. 
	There are many researches on displacement detection based on GNSS, which can be divided into two categories.

	%位移探测算法回顾，
	%传统位移探测的弊端
	%位移探测的短板1,关注与定位算法，忽略探测算法2，关注与longterm忽略shortterm
	%随着在线监测系统的普及，急需对于单历元动态监测数据进行分析处理，今早发现识别和确定位移。
	The first category is about the research of measurement technology in GNSS-based displacement detection.
	In order to evaluate the performance of single base station real time kinematic(RTK) and network RTK(NRTK) in displacement detection, the data of different observation duration were compared\cite{wang2011gps}. The results showed that NRTK has advantages in accuracy and robustness.
	A displacement monitoring system was designed to evaluate NRTK for displacement detection\cite{GUMUS2019131}. The results showed that NRTK can achieve an accuracy of 4.7 mm and 7.9 mm in the horizontal and vertical directions respectively.
	In \cite{csanliouglu2016landslide} and \cite{lytvyn2012real}, the feasibility of displacement detection for landslides  using PPP has been studied. The results showed that PPP can be capable of detecting large landslides.
	There are also some studies using the time-differenced carrier phases (TDCP) technique\cite{freda2015time,colosimo2011real} to obtain velocity estimates for displacement detection. This kind of method obtains displacement by integrating velocity, which is mainly used in displacement detection and extraction of large earthquakes.
	In general, the above research mainly focuses on how to improve the positioning accuracy, and the research on how to identify and extract the displacement from the coordinate sequence obtained by GNSS is limited.

@@

The displacement time series is described as $\left[ {{x_1},{x_2}, \cdots {x_m}} \right]$, and the corresponding time is denoted as $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$, where $m$ is the number of coordinate. The displacement occurrence time is expressed as $\left[ {{\tau _1},{\tau _2}, \cdots {\tau _n}} \right]$, which is a subset of $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$.  
The time corresponding to the $n$ change points satisfies the following relationship:$ {{\tau _1}<{\tau _2}<\cdots {\tau _{n-1}}<{\tau _n}} $.
The problem of displacement detection is to find out the time of displacement and estimate the displacement.

@@

\begin{equation}\label{eq_monte_carlo_1}
s =\sum\limits_x g(x)= \sum\limits_x {p(x)f(x) = {E_p}[f(x)]}
\end{equation}
\begin{equation}\label{eq_monte_carlo_2}
s =\int {g(x)}= \int {p(x)f(x)dx}  = {E_p}[f(x)]
\end{equation}
where $g(x)$ is the function to be integrated or summated; $p(x)$ is the probability distribution or probability density function of $x$. The integral or summation problem of $g(x)$ is transformed into the mathematical expectation problem of $f(x)$ under the distribution $p(x)$. This mathematical expectation can be approximated by sampling from $p(x)$\cite{goodfellow2016deep}.

@@

\subsection{Relative real-time kinematic (RTK)}
There are many real-time kinematic positioning models, among which RTK is the most widely used model in deformation monitoring.
Kalman filter is used in the implementation of  RTK, and the observation model, the state model, and the extended Kalman filtering process of RTK are introduced below. 
\subsubsection{Observation model}
The double-difference(DD) observation model is usually used in RTK, and its definition is shown in (\ref{eq_dd_obs})\cite{teunissen2017springer}.
\begin{figure*}
	\begin{equation}
	\left. \begin{array}{l}
	\Delta \nabla P_{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} - \Delta \nabla \delta I_{\Phi {i_{br}}}^{jk} + \Delta \nabla \delta _{tro{p_{br}}}^{jk} + \Delta \nabla \delta M_{{P_{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{P_{{i_{br}}}}}^{jk}\\
	\Delta \nabla \Phi _{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} + \Delta \nabla \delta I_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \delta _{tro{p_{br}}}^{jk} - {\lambda _i}\Delta \nabla N_{{i_{br}}}^{jk} + \Delta \nabla \delta M_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{\Phi _{{i_{br}}}}}^{jk}
	\end{array} \right\}
	\label{eq_dd_obs}
	\end{equation}
\end{figure*}
In this observation equation, $\Delta \nabla $ denotes the DD operator, $i$ denotes the frequency; $b$ and $r$ denote base station and rover station respectively; $j$ and $k$ represent the satellites;
$\Delta \nabla P_{{{i}_{br}}}^{jk}$ and $\Delta \nabla \Phi _{{{i}_{br}}}^{jk}$ denote pseudo-range and carrier-phase DD observations, respectively; 
$\Delta \nabla \rho _{br}^{jk}$ is the DD geometric distance between receivers and satellites; 
$\Delta \nabla \delta M_{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla \delta M_{{{\Phi }_{{{i}_{br}}}}}^{jk}$ denote pseudo-range and carrier-phase multipath error, respectively; 
$\Delta \nabla \varepsilon _{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla \varepsilon _{{{\Phi }_{{{i}_{br}}}}}^{jk}$ represent DD measurement noise of pseudo-range and carrier-phase, respectively; 
$\Delta \nabla \delta I_{\Phi {{i}_{br}}}^{jk}$is the DD ionospheric delay between receivers and satellites, and the ionospheric error has the same absolute value but the opposite sign on pseudo-range and carrier-phase observations\cite{teunissen2017springer}; $\Delta \nabla \delta _{tro{{p}_{br}}}^{jk}$is the DD tropospheric delay between receivers and satellites. 
For the short baseline, the atmospheric error can be ignored, so the above DD observation equation is simplified as (\ref{eq_dd_obs_simplified}).
\begin{figure*}
	\begin{equation}
	\left. \begin{array}{l}
	\Delta \nabla P_{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} + \Delta \nabla \delta M_{{P_{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{P_{{i_{br}}}}}^{jk}\\
	\Delta \nabla \Phi _{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} - {\lambda _i}\Delta \nabla N_{{i_{br}}}^{jk} + \Delta \nabla \delta M_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{\Phi _{{i_{br}}}}}^{jk}\end{array} \right\}
	\label{eq_dd_obs_simplified}
	\end{equation}

@@

After forming the observation equation, the ‘float’ solution of the parameter can be obtained by the standard least square method. 
The 'float' solution and variance of integer ambiguity are expressed as  $\Delta \nabla \mathbf{\tilde{N}} $,  ${{\mathbf{Q}}_{\Delta \nabla \mathbf{\tilde{N}}}} $, respectively. 
To obtain high precision positioning results, it is necessary to fix the integer ambiguity. 
Then the problem of ambiguity fixing can be described as (\ref{eq_lamda})\cite{teunissen1995the}.
\begin{figure*}
	\begin{equation}
	\Delta \nabla {\bf{\hat N}} = \mathop {\arg min}\limits_{\Delta \nabla {\bf{N}} \in {\bf{Z}}} ((\Delta \nabla {\bf{N}} - \Delta  {\bf{\tilde N}}){\bf{Q}}_{\Delta \nabla {\bf{\tilde N}}}^{ - 1}{(\Delta \nabla {\bf{N}} - \Delta \nabla {\bf{\tilde N}})^T})
	\label{eq_lamda}
	\end{equation}
\end{figure*}
There are many methods referring to integer ambiguity resolution, among which LAMBDA (Least-squares Ambiguity Decorrelation Adjustment)\cite{teunissen1995the} method is the most widely used one. The integer ambiguity is obtained by the integer least square method. Then, the test process is executed to determine whether to accept or reject the integer ambiguity\cite{teunissen2003integer,teunissen2005gnss}. If the test is passed, the fixed integer ambiguity can be substituted into (\ref{eq_rtk_measure}) to resolve the fixed solution, otherwise, the ‘float’ solution will be maintained.

\subsubsection{State model}
The state model is defined as follows (Takasu 2013)
\begin{equation}
{{\bf{x}}_k} = {\bf{F}}{{\bf{x}}_{k - 1}} + {\bf{w}}
\end{equation}
where ${\bf{F}} \buildrel \Delta \over = \left[ {\begin{array}{*{20}{c}}
	{{{\bf{I}}_{3 \times 3}}}&{\bf{0}}\\
	{\bf{0}}&{{{\bf{I}}_{(2n - 2)(2n - 2)}}}
	\end{array}} \right]$ , is the transition matrix from $k-1$ to $k$; $\mathbf{I}$ denotes the identity matrix; $n$ represents the number of satellites observed simultaneously by the base station and the rover station; 
Only GPS ${{L}_{1}}$ and ${{L}_{2}}$ frequency observations are considered, so $2n-2$ DD ambiguities are formed. 
$\mathbf{w}$ is the process noise, and its covariance matrix is expressed as ${{\mathbf{G}}_{w}}$. 
For kinematic positioning, the coordinate covariance component is set to be large to capture dynamic features, while the ambiguity covariance component is set to $\mathbf{0}$ to ensure the stability of positioning.
\subsubsection{Extended Kalman filtering}
Kalman filtering includes two processes: prediction update and measurement update\cite{grewal2001kalman}. The prediction process is as follows:
\begin{equation}
{{\bf{\hat x}}_{k|k - 1}} = {\bf{F}}{{\bf{\hat x}}_{k - 1}}
\end{equation}
\begin{equation}
{{\bf{Q}}_{k|k - 1}} = {\bf{F}}{{\bf{Q}}_{k - 1}}{{\bf{F}}^T} + {{\bf{G}}_w}(k)
\end{equation}
According to the definition of the state transition matrix above, it can be seen that the state value of the previous epoch remains unchanged. However, the coordinate covariance component becomes larger, while the ambiguity covariance component remains unchanged. The measurement update process is as follows:
\begin{equation}
{{\bf{v}}_k} = {\bf{y}}(k) - {\bf{H}}(k){{\bf{\hat x}}_{k|k - 1}}
\end{equation}
\begin{equation}
{{\bf{S}}_k} = {\bf{H}}(k){{\bf{Q}}_{k|k - 1}}{\bf{H}}{(k)^{\rm{T}}} + {{\bf{R}}_\varepsilon }(k)
\end{equation}
\begin{equation}
{\bf{K}} = {{\bf{Q}}_{k|k - 1}}{\bf{H}}_k^T{\bf{S}}_k^{ - 1}
\end{equation}
where ${{\mathbf{v}}_{k}}$ denotes the innovation vector, and ${{\mathbf{S}}_{k}}$ is the covariance matrix of the innovation vector; $\mathbf{K}$ is the state estimation gain matrix. The final state is estimated as follows:
\begin{equation}
{{\bf{\hat x}}_k} = {{\bf{\hat x}}_{k|k - 1}} + {\bf{K}}{{\bf{v}}_k}
\end{equation}
\begin{equation}
{{\bf{Q}}_k} = {{\bf{Q}}_{k|k - 1}} - {\bf{K}}{{\bf{S}}_k}{{\bf{K}}^T}
\end{equation}
where ${{\mathbf{\hat{x}}}_{k}}$ is the final estimate, and ${{\mathbf{Q}}_{k}}$ is the corresponding covariance matrix; ${{\mathbf{\hat{x}}}_{k}}$ is the only input of the proposed method.

>>>>

	% As a general rule, do not put math, special symbols or citations
	% in the abstract or keywords.
	\begin{abstract}
For decades, displacement detection based on the Global navigation satellite system (GNSS) has increasingly been important for a wide range of applications, from landslide monitoring, subsidence survey, to industrial measurement. 
Most of the GNSS-based displacement detection methods in these applications are based on GNSS long-term static positioning results.
With the development of Internet of Things (IoT), high-precision GNSS positioning, and GNSS related transmission protocol, kinematic positioning results can be transmitted to the cloud in real-time.
However, due to the influence of measurement noise, it is still a challenge to identify and extract displacement from GNSS kinematic positioning results in a short time.
To resolve this, we propose a novel displacement detection approach with the purpose of identifying and extracting displacement from GNSS kinematic positioning.
Specifically, we use the Bayesian inference model to obtain the displacement change time from the coordinate time series of GNSS kinematic positioning. 
%The likelihood function of the observation and the prior distribution of the parameters to be estimated are provided.
%Finally, Bayesian inference was implemented by Markov Chain Monte Carlo (MCMC) sampling.
By investigating the posterior distribution of the designed change point parameter, we can identify the change points.
Furthermore, we derive the mean value from the posterior distribution of the mean parameter, and further obtain the displacement.
Results from simulation and field experiments have demonstrated the effectiveness and flexibility of the proposed method.
For significant displacement, it can be clearly identified; for small displacement, it can be identified by adding an interval constraint prior. The accuracy of up-displacement extraction from GNSS real-time kinematic positioning can reach within 2 mm in 15 minutes.
	\end{abstract}

@@

	\section{Introduction}
	% The very first letter is a 2 line initial drop letter followed
	% by the rest of the first word in caps.
	% 
	% form to use if the first word consists of a single letter:
	% \IEEEPARstart{A}{demo} file is ....
	% 
	% form to use if you need the single drop letter followed by
	% normal text (unknown if ever used by the IEEE):
	% \IEEEPARstart{A}{}demo file is ....
	% 
	% Some journals put the first two words in caps:
	% \IEEEPARstart{T}{his demo} file is ....
	% 
	% Here we have the typical use of a "T" for an initial drop letter
	% and "HIS" in caps to complete the first word.
	\label{intro}
	%全球定位系统系统的应用-》位移探测
	%在自然灾害监测，或者工业测量等领域，GNSS被用于位移探测。
	%传统测量仪器的弊端，GNSS位移探测的优势。
	%GNSS在位移探测中扮演的角色，以及位移探测的要求
	%目前人们对于基于GNSS位移探测的研究更过的关注与如何提高定位的精度，而忽略了如何从GNSS获取的坐标序列中识别并提取位移。
	\IEEEPARstart{I}{n}  recent decades, the Global navigation satellite system (GNSS) has been widely used in surveying\cite{barry2011surveying}, civil aviation\cite{iatsouk2004development}, and autonomous vehicle\cite{kuutti2018survey} as a positioning method. 
	Besides, as a displacement detection method in deformation monitoring, GNSS has been applied to landslide monitoring\cite{awange2012environmental}, subsidence survey\cite{bian2014monitoring}, industrial measurement\cite{pavasovic2011application}, and other fields. 
	Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high precision, and weather independence\cite{shen2019a}. 
	%随着物联网通信技术标准的制订和创新，高精度定位技术，例如RTK，PPP，以及GNSS传输协议NTRIP的发展，GNSS定位结果可以被实时传输到云端。
	With the development of the Internet of things (IoT), GNSS high-precision positioning technology, and GNSS enhanced information transmission protocol, high-precision GNSS positioning results can be transmitted to the cloud in real-time\cite{mei2019survey}.
	%Displacement detection involves displacement identification and extraction. 
	GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results\cite{abidin2004use,rs12203375}. 
	There are many researches on displacement detection based on GNSS, which can be divided into two categories.

	%位移探测算法回顾，
	%传统位移探测的弊端
	%位移探测的短板1,关注与定位算法，忽略探测算法2，关注与longterm忽略shortterm
	%随着在线监测系统的普及，急需对于单历元动态监测数据进行分析处理，今早发现识别和确定位移。
	The first category is about the research of measurement technology in GNSS-based displacement detection.
	In order to evaluate the performance of single base station real time kinematic(RTK) and network real time kinematic(NRTK) in displacement detection, the data of different observation duration were compared\cite{wang2011gps}. The results showed that NRTK has advantages in accuracy and robustness.
	A displacement monitoring system was designed to evaluate NRTK for displacement detection\cite{GUMUS2019131}. The results showed that NRTK can achieve an accuracy of 4.7 mm and 7.9 mm in the horizontal and vertical directions respectively.
	In \cite{csanliouglu2016landslide} and \cite{lytvyn2012real}, the feasibility of displacement detection for landslides  using precise point position(PPP) has been studied. The results showed that PPP can be capable of detecting large landslides.
	There are also some studies using the time-differenced carrier phases (TDCP) technique\cite{freda2015time,colosimo2011real} to obtain velocity estimates for displacement detection. This kind of method obtains displacement by integrating velocity, which is mainly used in displacement detection and extraction of large earthquakes.
	In general, the above research mainly focuses on how to improve the positioning accuracy, and the research on how to identify and extract the displacement from the coordinate sequence obtained by GNSS is limited.

@@

The displacement time series is described as $\left[ {{x_1},{x_2}, \cdots {x_m}} \right]$, and the corresponding time is denoted as $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$, where $m$ is the number of coordinate. The displacement occurrence time is expressed as $\left[ {{\tau _1},{\tau _2}, \cdots {\tau _n}} \right]$, which is a subset of $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$.  
The time corresponding to the $n$ change points satisfies the following relationship: $ {{\tau _1}<{\tau _2}<\cdots {\tau _{n-1}}<{\tau _n}} $.
The problem of displacement detection is to find out the time of displacement and estimate the displacement.

@@

\begin{equation}\label{eq_monte_carlo_1}
s =\sum\limits_x g(x)= \sum\limits_x {p(x)f(x) = {E_p}[f(x)]}
\end{equation}
\begin{equation}\label{eq_monte_carlo_2}
s =\int {g(x)dx}= \int {p(x)f(x)dx}  = {E_p}[f(x)]
\end{equation}
where $g(x)$ is the function to be integrated or summated; $p(x)$ is the probability distribution or probability density function of $x$. The integral or summation problem of $g(x)$ is transformed into the mathematical expectation problem of $f(x)$ under the distribution $p(x)$. This mathematical expectation can be approximated by sampling from $p(x)$\cite{goodfellow2016deep}.

@@

\subsection{Relative Real-time Kinematic (RTK)}
There are many real-time kinematic positioning models, among which RTK is the most widely used model in deformation monitoring.
Kalman filter is used in the implementation of  RTK, and the observation model, the state model, and the extended Kalman filtering process of RTK are introduced below. 
\subsubsection{Observation Model}
The double-difference(DD) observation model is usually used in RTK, and its definition is shown in (\ref{eq_dd_obs})\cite{teunissen2017springer}.
\begin{figure*}
	\begin{equation}
	\left. \begin{array}{l}
	\Delta \nabla P_{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} - \Delta \nabla I_{\Phi {i_{br}}}^{jk} + \Delta \nabla  T_{br}^{jk} + \Delta \nabla  M_{{P_{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{P_{{i_{br}}}}}^{jk}\\
	\Delta \nabla \Phi _{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} + \Delta \nabla I_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla T_{br}^{jk} - {\lambda _i}\Delta \nabla N_{{i_{br}}}^{jk} + \Delta \nabla  M_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{\Phi _{{i_{br}}}}}^{jk}
	\end{array} \right\}
	\label{eq_dd_obs}
	\end{equation}
\end{figure*}
In this observation equation, $\Delta \nabla $ denotes the DD operator, $i$ denotes the frequency; $b$ and $r$ denote base station and rover station respectively; $j$ and $k$ represent the satellites;
$\Delta \nabla P_{{{i}_{br}}}^{jk}$ and $\Delta \nabla \Phi _{{{i}_{br}}}^{jk}$ denote pseudo-range and carrier-phase DD observations, respectively; 
$\Delta \nabla \rho _{br}^{jk}$ is the DD geometric distance between receivers and satellites; 
$\Delta \nabla  M_{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla  M_{{{\Phi }_{{{i}_{br}}}}}^{jk}$ denote pseudo-range and carrier-phase multipath error, respectively; 
$\Delta \nabla \varepsilon _{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla \varepsilon _{{{\Phi }_{{{i}_{br}}}}}^{jk}$ represent DD measurement noise of pseudo-range and carrier-phase, respectively; 
$\Delta \nabla  I_{\Phi {{i}_{br}}}^{jk}$is the DD ionospheric delay between receivers and satellites, and the ionospheric error has the same absolute value but the opposite sign on pseudo-range and carrier-phase observations\cite{teunissen2017springer}; $\Delta \nabla T_{br}^{jk}$is the DD tropospheric delay between receivers and satellites. 
For the short baseline, the atmospheric error can be ignored, so the above DD observation equation is simplified as (\ref{eq_dd_obs_simplified}).
\begin{figure*}
	\begin{equation}
	\left. \begin{array}{l}
	\Delta \nabla P_{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} + \Delta \nabla  M_{{P_{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{P_{{i_{br}}}}}^{jk}\\
	\Delta \nabla \Phi _{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} - {\lambda _i}\Delta \nabla N_{{i_{br}}}^{jk} + \Delta \nabla  M_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{\Phi _{{i_{br}}}}}^{jk}\end{array} \right\}
	\label{eq_dd_obs_simplified}
	\end{equation}

@@

After forming the observation equation, the ‘float’ solution of the parameter can be obtained by the standard least square method. 
The 'float' solution and variance of integer ambiguity are expressed as  $\Delta \nabla \mathbf{\tilde{N}} $,  ${{\mathbf{Q}}_{\Delta \nabla \mathbf{\tilde{N}}}} $, respectively. 
To obtain high precision positioning results, it is necessary to fix the integer ambiguity. 
The problem of ambiguity fixing can be described as (\ref{eq_lamda})\cite{teunissen1995the}.
\begin{figure*}
	\begin{equation}
	\Delta \nabla {\bf{\hat N}} = \mathop {\arg min}\limits_{\Delta \nabla {\bf{N}} \in {\bf{Z}}} ((\Delta \nabla {\bf{N}} - \Delta  {\bf{\tilde N}}){\bf{Q}}_{\Delta \nabla {\bf{\tilde N}}}^{ - 1}{(\Delta \nabla {\bf{N}} - \Delta \nabla {\bf{\tilde N}})^T})
	\label{eq_lamda}
	\end{equation}
\end{figure*}
There are many methods referring to integer ambiguity resolution, among which LAMBDA (Least-squares Ambiguity Decorrelation Adjustment)\cite{teunissen1995the} method is the most widely used one. The integer ambiguity is obtained by the integer least square method. Then, the test process is executed to determine whether to accept or reject the integer ambiguity\cite{teunissen2003integer,teunissen2005gnss}. If the test is passed, the fixed integer ambiguity can be substituted into (\ref{eq_rtk_measure}) to resolve the fixed solution, otherwise, the ‘float’ solution will be maintained.

\subsubsection{State Model}
The state model is defined as follows (Takasu 2013)
\begin{equation}
{{\bf{x}}_k} = {\bf{F}}{{\bf{x}}_{k - 1}} + {\bf{w}}
\end{equation}
where ${\bf{F}} \buildrel \Delta \over = \left[ {\begin{array}{*{20}{c}}
	{{{\bf{I}}_{3 \times 3}}}&{\bf{0}}\\
	{\bf{0}}&{{{\bf{I}}_{(2n - 2)(2n - 2)}}}
	\end{array}} \right]$ , is the transition matrix from $k-1$ to $k$; $\mathbf{I}$ denotes the identity matrix; $n$ represents the number of satellites observed simultaneously by the base station and the rover station; 
Only GPS ${{L}_{1}}$ and ${{L}_{2}}$ frequency observations are considered, so $2n-2$ DD ambiguities are formed. 
$\mathbf{w}$ is the process noise, and its covariance matrix is expressed as ${{\mathbf{G}}_{w}}$. 
For kinematic positioning, the coordinate covariance component is set to be large to capture dynamic features, while the ambiguity covariance component is set to $\mathbf{0}$ to ensure the stability of positioning.
\subsubsection{Extended Kalman filtering}
Kalman filtering includes two processes: prediction update and measurement update\cite{grewal2001kalman}. The prediction process is as follows:
\begin{equation}
{{\bf{\hat x}}_{k|k - 1}} = {\bf{F}}{{\bf{\hat x}}_{k - 1}}
\end{equation}
\begin{equation}
{{\bf{Q}}_{k|k - 1}} = {\bf{F}}{{\bf{Q}}_{k - 1}}{{\bf{F}}^T} + {{\bf{G}}_w}(k)
\end{equation}
According to the definition of the state transition matrix above, it can be seen that the state value of the previous epoch remains unchanged. However, the coordinate covariance component becomes larger, while the ambiguity covariance component remains unchanged. The measurement update process is as follows:
\begin{equation}
{{\bf{v}}_k} = {\bf{y}}(k) - {\bf{H}}_k{{\bf{\hat x}}_{k|k - 1}}
\end{equation}
\begin{equation}
{{\bf{S}}_k} = {\bf{H}}_k{{\bf{Q}}_{k|k - 1}}{\bf{H}}{_k^{\rm{T}}} + {{\bf{R}}_\varepsilon }(k)
\end{equation}
\begin{equation}
{\bf{K}} = {{\bf{Q}}_{k|k - 1}}{\bf{H}}_k^T{\bf{S}}_k^{ - 1}
\end{equation}
where ${{\mathbf{v}}_{k}}$ denotes the innovation vector, and ${{\mathbf{S}}_{k}}$ is the covariance matrix of the innovation vector; $\mathbf{K}$ is the state estimation gain matrix. The final state is estimated as follows:
\begin{equation}
{{\bf{\hat x}}_k} = {{\bf{\hat x}}_{k|k - 1}} + {\bf{K}}{{\bf{v}}_k}
\end{equation}
\begin{equation}
{{\bf{Q}}_k} = {{\bf{Q}}_{k|k - 1}} - {\bf{K}}{{\bf{S}}_k}{{\bf{K}}^T}
\end{equation}
where ${{\mathbf{\hat{x}}}_{k}}$ is the final estimate, and ${{\mathbf{Q}}_{k}}$ is the corresponding covariance matrix; ${{\mathbf{\hat{x}}}_{k}}$ is the only input of the proposed method.
